---
title: "Homework 8"
output: github_document
---
### Question 1
Plotting the relationship of price as a function of weight for each color in order of decreasing slope for the *diamonds* data set.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(modelr)

ggplot(data = diamonds) +
  geom_point(aes(x=carat, y=price, color = color))

# plotting general relationship between carat and price for the whole data set

dmd <- diamonds %>%
  group_by(color) %>%
  nest()

# grouping by color and listing the data via nest
```
```{r, message=FALSE, warning=FALSE}
color_model <- function(df)
  lm(price~carat, data = df)
# Creating the linear model and primary function df

dmd <- dmd %>%
  mutate(model = map(data, color_model))

dmd <- dmd %>%
  mutate(predicts = map2(data, model, add_predictions))

predicts <- unnest(dmd, predicts)

# unnesting the list in order to plot the data
```


```{r, message=FALSE, warning=FALSE}
ggplot(data = predicts) +
  geom_line(aes(x=carat, y=pred)) +
  geom_point(aes(x=carat, y=price)) +
  facet_wrap(~color)

arrange(predicts, desc(color))

```

### Question 2

Fitting nonlinear models using either a monod model or a single square root model and comparing the effectiveness of both at displaying the DNase data set. 

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(data=DNase) +
  geom_point(aes(conc, density))
# Showing conc and density are not related in a linear way.
```
```{r, message=FALSE, warning=FALSE}
library(nls2)
library(proto)

by_run <- DNase %>% 
  group_by(Run) %>% 
  nest()
nls_mod <- formula(density ~ beta_1 * sqrt(conc) + beta_0)
single_sqrt_model <- function(ssm) {
  nls2(nls_mod, 
  data = ssm, 
  start = list(beta_1 = 0.5, beta_0 = 0.1))
}
by_run <- by_run %>% 
  mutate(model = map(data, single_sqrt_model ))
glance <- by_run %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)
ggplot(glance, aes(x=Run, y=AIC)) + 
  geom_point() + 
  ggtitle("Square root model")+
 scale_x_discrete(limits=glance$Run)

# Creating the square root model
```
```{r, message=FALSE, warning=TRUE}

by_run_2 <- DNase %>% 
  group_by(Run) %>% 
  nest()
mon_mod <- formula(density ~ beta_3*conc / (beta_4+conc))
monod_model <- function(mm) {
  nls2(mon_mod, 
  data = mm, 
  start = list(beta_3 = 2, beta_4 = 3))
}
by_run_2 <- by_run_2 %>% 
  mutate(model = map(data, monod_model ))
glance <- by_run_2 %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)
ggplot(glance, aes(x=Run, y=AIC)) + 
  geom_point() + 
  ggtitle("Monod-type model")+
 scale_x_discrete(limits=glance$Run)

# Creating the monod model and defining the variables Dmax and K

```

Based on the shapes of the plots, it appears that the monod-type model is the better of the two to display the data.